\chapter{Sides}

\section{Hash Brown Potatoes\index{sides!hash brown potatoes}}

\begin{open}
  Contributed by Joyce Evans. Try with the Swiss Meatloaf
  (Section~\ref{sec:swiss-meatloaf}), yum! Serves 4.
\end{open}
\begin{ingredients}
  3 large potatoes, boiled \\
  \SI{1/4}{\cup} milk \\
  \SI{3}{\tblspoon} all-purpose flour \\
  \SI{2}{\tblspoon} minced onion \\
  \SI{2}{\tblspoon} minced fresh parsley or chervil \\
  \SI{1/2}{\teaspoon} salt \\
  \SI{1/2}{\teaspoon} pepper \\
  \SI{1/4}{\teaspoon} dried oregano (opt.) \\
  Dash of Tabasco \\
  \SI{3}{\tblspoon} bacon drippings, rendered chicken fat, or vegetable oil
\end{ingredients}
Preheat in electric skillet to \SI{300}{\degree}. Peel and dice the boiled
potatoes and place into a medium bowl. You should have about \SI{3}{\cup}. Add
the rest of the ingredients except the cooking fat and blend.

Add the cooking fat to the skillet and heat. Pack the potato mixture in
firmly, spreading it out in an even layer. Cook \numrange{7}{9} minutes or
until the bottom side is richly brown. Turn the mixture over in segments and
smooth down again into a patty. Continue cooking until the other side is
brown, another \numrange{7}{9} minutes.  Cut into wedges and serve.

\section{Black Rice\index{sides!black rice}}

\begin{open}
  Contributed by Fermina Evans. Serves 4, or 2 healthy eaters. This is Tom and
  Katie's favorite peasant food.
\end{open}
\begin{ingredients}
  \SI{1}{\cup} dry black beans\\
  \SI{5}{\cup} chicken broth\\
  \SI{1/2}{\tblspoon} olive oil \\
  1 small onion, chopped \\
  4 cloves garlic, minced \\
  \SI{1}{\ounce} finely chopped Canadian or regular bacon \\
  \SI{1/2}{\cup} rice \\
  \SI{1/4}{\cup} white wine \\
  1 tomato coarsely chopped \\
  \SI{1/2}{\teaspoon} ground cumin \\
  pinch cayenne \\
  \SI{1/2}{\cup} finely chopped cilantro
\end{ingredients}
You may substitute 2 cans black beans for dry beans if you prefer. If using
dry beans, soak beans overnight in cold water, and simmer beans for
\numrange{120}{150} minutes in \SI{3}{\cup} broth until tender. Drain and
resolve liquid (\SI{1/2}[1]{\cup}). Otherwise, drain them under cold water and
use \SI{1/2}[1]{\cup} chicken broth or chicken bouillon stock for bean broth.

Heat oil in stockpot. Add onion, garlic, and bacon and stir fry for about 5
minutes.  Add rice and stir for 1 minute. Add wine and cook for 2 minutes. Add
tomatoes and cook for 2 more minutes.  Add bean broth \SI{1/2}{\cup} at a
time, stirring until liquid is absorbed before adding more broth. This will
take \numrange{20}{25} minutes to complete. Add the beans and remaining
broth. Season with cumin, cayenne, and cilantro and serve.

\section{Potato Gratin with Mustard and Cheese\index{sides!Potato Gratin}}

\begin{open}
  This is a great entertaining dish because its classy, very smooth and
  flavorful, yet can be prepared before guests arrive. Kate got it from
  \corp{Bon Appetit} magazine.
\end{open}
\begin{ingredients}
  \SI{1}{\tblspoon} butter\\
  \SI{1}{\cup} fresh breadcrumbs\\
  \SI{1}{\tblspoon} dried thyme\\
  \SI{2}{\teaspoon} salt\\
  \SI{1}{\teaspoon} ground pepper\\
  \SI{1}{\pound} sharp white cheddar cheese, grated\\
  \SI{1/4}{\cup} flour\\
  \SI{5}{\pound} russet potatoes, peeled and thinly sliced\\
  \SI{4}{\cup} canned low salt chicken broth\\
  \SI{1}{\cup} whipping cream\\
  \SI{6}{\tblspoon} Dijon mustard
\end{ingredients}
Melt butter in skillet and add breadcrumbs, stirring until golden brown (about
10 min.). Set aside. Preheat oven to \SI{400}{\degree}. Butter a
\SI{15x10x2}{\inch} baking dish. Mix thyme, salt, and pepper in small
bowl. Combine grated cheese and flour, tossing to coat the cheese. Arrange
\num{1/3} potato slices to cover the bottom of the baking dish. Sprinkle
\num{1/3} the thyme mixture, then \num{1/3} the cheese mixture. Repeat
layering 2 more times.  Next whisk chicken broth, cream, and mustard in a
separate bowl, and then pour it over the potato layers. Bake 30
minutes. Sprinkle buttered crumbs over, and bake until potatoes are tender and
top is golden brown, about 1 hour longer.  Enjoy!
