\chapter{Treats}

\section{Mint Syrup\index{treats!mint syrup}}

\begin{open}
    This recipe comes from Louise Johnson of Spruce Head, ME, aka Weedie, the sister of the original Donald Dodge Johnson (Dodge and Julie’s father).
\end{open}
%%
\begin{ingredients}
    fresh spearmint or peppermint leaves\\
    granulated sugar\\
    1 or more lemons\\
    1 or more oranges\\
\end{ingredients}
Using a strainer that fits into a deep bowl, fill with finely cut fresh spearmint or peppermint leaves. Boil for ten minutes equal measures of water and granulated sugar, approximately 1\SI{1/2}{\cup} each. Pour directly over the mint and allow to cool. Remove the strainer and add the juice of one or more lemons and the juice of one or more oranges. Wonderful over ice cream, in iced tea, or on a simple cake aching for a hint of mint.

\section{Southern Pecan Pie\index{treats!southern pecan pie}}

\begin{open}
    Hey y'all from Martha, this is from an ancient out of print Better Homes and
    Garden Cookbook One can double the sin by brushing the crust with a dark
    chocolate glaze before adding the filling, but it's pretty wonderful as is!
    And so easy! Either a pie crust mix, or the real thing work equally well.
    The main thing is to have fresh pecans.
\end{open}
%%
\begin{ingredients}
    3 large eggs\\
    \SI{2/3}{\cup} sugar\\
    \SI{1}{\cup} dark corn syrup\\
    \SI{1/3}{\cup} melted butter\\
    \SI{1}{\cup} pecan halves\\
    1 \SI{9}{\inch} unbaked pastry shell\\
\end{ingredients}
Beat eggs thoroughly with sugar, a dash of salt, corn syrup, and melted butter.
Add pecans. (Brush shell with melted chocolate if desired). Bake in moderate
oven (\SI{350}{\degreeF}) \SI{50}{\minute} or until a knife inserted near center
comes out clean. Cool.

\section{Grapes \`{a} la Creme\index{treats!grapes a la creme}}

\begin{open}
    This is from Paul Horne's mother, Mildred W. Horne, Alexandra, VA, 1959.
\end{open}
%%
\begin{ingredients}
    seedless grapes\\
    sour cream\\
    brown sugar\\
\end{ingredients}
Wash and de-stem 1\SIrange{1/2}{2}{\pound} of grapes. Drain and place in dessert
dishes, preferably long-stemmed ones.  Spread a tablespoon or so of sour cream
over each mound of grapes and leave in refrigerator for several hours.  An hour
or so before dinner, sprinkle liberally with brown sugar and replace in
refrigerator until dessert time.  Serve with coffee.