\chapter{Sides}

\section{White Grapes and Sweetened ``Cream''\index{sides!white grapes and
sweetened cream}}
\index{Lindquist!Julie}

\begin{open}
Here is a refreshing and simple summery side submitted by Julie Lindquist.
\end{open}
%%
\begin{ingredients}
    grapes\\
    plain yogurt or sour cream\\
    brown sugar
\end{ingredients}
Remove grapes from stems; rinse and dry. Place in a colorful serving dish. Top
with plain yogurt or sour cream (NB: sweet cream doesn't offer the contrast to
the sweet grape taste). Sprinkle some brown sugar on top. Refrigerate for at
least 4 hours; the attractive pattern of the dissolving brown sugar is a
bonus. Lasts a few days, if there’s any left.

\section{Turkish Rice\index{sides!turkish rice}}
\index{Johnson!Martha}
\index{Johnson!Dodge}

\begin{open}
    From Martha and Dodge, a graduate school special that provides an infinitely
    variable way to prepare a pilaf with your favorite spices and ingredients.
\end{open}
%%
\begin{ingredients}
    chopped onion or shallot\\
    \SI{1}{\cup} long grain rice\\
    2\SI{1/3}{\cup} beef bouillon\\
    raisins, dried cranberries, nuts\\
    cumin, curry powder, garlic
\end{ingredients}
Cook a few tablespoons of chopped onion or shallot in some butter and oil. Add
uncooked rice and stir until light brown. Add the beef bouillon, plus a handful
of raisins, dried cranberries, nuts and seasonings (some mix of cumin, curry
powder, garlic, etc.) and simmer until done (\SI{20}{\minute}).

\section{Boursin Potatoes\index{sides!boursin potatoes}}
\index{Johnson!Martha}

\begin{open}
    From Martha: a favorite side from Barby Buckman at St.~Peter's in the Great
    Valley, PA. A great dish for a crowd (8), or a half recipe also works well
    for 4.
\end{open}
%%
\begin{ingredients}
    \SI{2}{\cup} whipping cream\\
    1 \SI{5}{\ounce} ounce package Boursin cheese (herbs)\\
    \SI{3}{\pound} red new potatoes, or Yukon Gold, unpeeled, scrubbed and
    thinly sliced\\
    salt and pepper\\
    \SIrange{1}{2}{\tblspoon} chopped fresh parsley
\end{ingredients}
Preheat oven to \SI{400}{\degreeF}. Stir whipping cream and Bousing cheese in a
heavy pan over medium heat until cheese melts and no lumps remain. Arrange half
the potatoes in overlapping rows in a buttered \SI{9x13}{\inch} baking dish.
Season with salt and pepper and pour half the cheese mixture over them. Arrange
the rest of the potatoes in a second layer with remaining cheese mix. Bake until
golden brown, about \SI{1}{\hour}. Sprinkle with parsley and serve.

\section{Immune-Boosting Chimichurri from Argentina}
\index{sides!immune-boosting chimichurri}
\index{Rona!Alison}

\begin{open}
    Chimichurri is basically Argentinian pesto.  You can use it on everything
    from meat dishes, vegetables, salads, and breads.  According to Alison Rona,
    ``This will make any meat taste great!''
\end{open}
%%
\begin{ingredients}
    1 large bunch of flat leafed parsley chopped\\
    1 large bunch of fresh oregano leaves stripped from stems\\
    1 large bunch of fresh cilantro all chopped\\
    1 green jalape\~{n}o pepper chopped\\
    1 small yellow onion (or shallots) chopped\\
    1 lemon (I cut off most of the rind, cut it in half, take out the seeds, and
    throw both halves in the blender)\\
    6 large cloves of garlic chopped finely\\
    \SIrange{2}{3}{\tblspoon} of red wine vinegar to taste\\
    \SIrange{3}{4}{\tblspoon} olive oil\\
    sea salt and black pepper
\end{ingredients}
Throw everything in a blender and mix.