\chapter{Sides}

\section{Hash Brown Potatoes\index{sides!hash brown potatoes}}

\textit{Contributed by Joyce Evans. Try with the Swiss Meatloaf 
(Section~\ref{sec:swiss-meatloaf}), yum! Serves 4}.
\begin{ingredients}
3 large potatoes, boiled \\
1/4 cup milk \\
3 Tbsp. all-purpose flour \\
2 Tbsp. minced onion \\
2 Tbsp. minced fresh parsley or chervil \\
1/2 tsp. salt \\
1/2 tsp. pepper \\
1/4 tps dried oregano (opt.) \\
Dash of tabasco \\
3 Tbsp. bacon drippings, rendered chicken fat, or vegetable oil
\end{ingredients}
Preheat in electric skillet to \oven{300}. Peel and dice the boiled potatoes
and place into a medium bowl. You should have about 3 cups. Add the rest of the
ingredients except the cooking fat and blend. 

Add the cooking fat to the skillet and heat. Pack the potato mixture in firmly,
spreading it out in an even layer. Cook 7-9 minutes or until the bottom side is
richly brown. Turn the mixture over in segments and smooth down again into a
patty. Continue cooking until the other side is brown, another 7-9 minutes.
Cut into wedges and serve.

\section{Black Rice\index{sides!black rice}}

\textit{Contributed by Fermina Evans. Serves 4, or 2 healthy eaters. This is
Tom and Katie's favorite peasant food.}
\begin{ingredients}
1 cup dry black beans\\
5 cups chicken broth\\
1/2 Tbsp. olive oil \\
1 small onion, chopped \\
4 cloves garlic, minced \\
1 oz finely chopped canadian or regular bacon \\
1/2 cup rice \\
1/4 cup white wine \\
1 tomato coarsely chopped \\
1/2 tsp. ground cumin \\
pinch cayenne \\
1/2 cup finely chopped cilantro
\end{ingredients}
You may substitue 2 cans black beans for dry beans if you prefer. If using dry
beans, soak beans overnight in cold water, and simmer beans for 2-2 1/2 hours in
3 cups broth until tender. Drain and resolve liquid (1 1/2 cups). Otherwise,
drain them under cold water and use 1 1/2 cup chicken broth or chicken
boullion stock for bean broth.  

Heat oil in stockpot. Add onion, garlic, and bacon and stir fry for about 5
minutes.  Add rice and stir for 1 minute. Add wine and cook for 2 minutes. Add
tomaotes and cook for 2 more minutes.  Add bean broth 1/2 cup at a time,
stirring until liquid is absorbed before adding more broth. This will take
20-25 minutes to complete. Add the beans and remaining broth. Season with cumin,
cayenne, and cilantro and serve. 

\section{Potato Gratin with Mustard and Cheese\index{sides!Potato Gratin}}

\textit{This is a great entertaining dish because its classy, very smooth and
flavorful, yet can be prepared before guests arrive. Kate got it from}
\corp{Bon Appetit} \textit{magazine.}
\begin{ingredients}
1 Tbsp. butter\\
1 cup fresh breadcrumbs\\
1 Tbsp. dried thyme\\
2 tsp. salt\\
1 tsp. ground pepper\\
1 lb. sharp white cheddar cheese, grated\\
1/4 cup flour\\
5 lbs. russet potatoes, peeled and thinly sliced\\
4 cups canned low salt chicken broth\\
1 cup whipping cream\\
6 Tbsp. Dijon mustard
\end{ingredients}
 Melt butter in skillet and add breadcrumbs, stirring until golden brown (about
10 min.). Set aside. Preheat oven to \oven{400}. Butter a 
$15''\times 10''\times 2''$ inch baking
dish. Mix thyme, salt, and  pepper in small bowl. Combine grated cheese and
flour, tossing to coat the cheese. Arrange 1/3 potato slices to cover the
bottom of the baking dish. Sprinkle 1/3 the thyme mixture, then 1/3 the
cheese mixture. Repeat layering 2 more times.  Next whisk chicken broth,
cream, and mustard in a separate bowl, and then pour it over the potato
layers. Bake 30 minutes. Sprinkle buttered crumbs over, and bake until
potatoes are tender and top is golden brown, about 1 hour longer.  Enjoy!    
